### 2020-07-28 text/content.tex
Add more details to DAS
Resolves #15

\section*{Data Availability Statement}
The mobility data used in this paper \cite{SafeGraph2020-gn} is proprietary, but may be obtained free of charge for COVID-19-related research from the COVID-19 Consortium. The authors are not affiliated with this consortium. Researchers interested in access to the data can apply at \url{https://www.safegraph.com/covid-19-data-consortium}. After signing a Data Agreement, access is granted within a few days. The Consortium does not require coauthorship and does not preview or approve research reports before publication. Datafiles used: \texttt{/monthly-patterns/patterns\_backfill/2020/05/07/12/2020/02/ patterns-part[1-4].csv.gz} (data for February 2020, released May 7, 2020) and \texttt{/monthly-patterns/patterns/2020/06/05/06/patterns-part[1-4].csv.gz} (data for February 2020, released June 5, 2020). The authors will assist with any reasonable replication attempts for two years following publication.

>>>>

\section*{Data Availability Statement}
The mobility data used in this paper \cite{SafeGraph2020-gn} is proprietary, but may be obtained free of charge for COVID-19-related research from the COVID-19 Consortium. The authors are not affiliated with this consortium. Researchers interested in access to the data can apply at \url{https://www.safegraph.com/covid-19-data-consortium} (data manager: Ross Epstein, ross@safegraph.com). After signing a Data Agreement, access is granted within a few days. The Consortium does not require coauthorship and does not review or approve research results before publication. Datafiles used: \texttt{/monthly-patterns/patterns\_backfill/2020/05/07/12/2020/02/ patterns-part[1-4].csv.gz} (data for February 2020, released May 7, 2020) and \texttt{/monthly-patterns/patterns/2020/06/05/06/patterns-part[1-4].csv.gz} (data for February 2020, released June 5, 2020). The COVID-19 Consortium will keep these datafiles accessible for researchers. The authors will assist with any reasonable replication attempts for two years following publication.
